### 2024-10-22 Manuscript/supplementaries.tex
Update supplementaries.tex

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{Figures/raw_results_per_metric_per_stressor_emp.pdf}
\caption{\scriptsize{\textbf{Raw metric scores for the empirical data:} the y axes represent the different metrics tested (sorted by categories).
The different columns represent the different stressors.
The x-axes represent the scaled metric scores.
The dots represent the median metric value, the full line their 50\% confidence interval (CI) and the dashed line their 95\% CI.
The colours are here to visually separate the metrics by categories (blue = regularity, yellow = divergence, green = richness); the colour gradient within each row corresponds to a removal of respectively 80\%, 60\%, 40\% and 20\% of the data (from top to bottom).
\textbf{NOTE: for the \texttt{TPD} metrics, the metric is calculated using the 4 first dimensions only.}
}}
\label{Fig:raw_results_emp}
\end{figure}
\bigskip

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.6\textwidth]{Figures/raw_results_per_metric_per_stressor_emp.pdf}
\caption{\scriptsize{\textbf{Raw metric scores for the empirical data:} the y axes represent the different metrics tested (sorted by categories).
The different columns represent the different stressors.
The x-axes represent the scaled metric scores.
The dots represent the median metric value, the full line their 50\% confidence interval (CI) and the dashed line their 95\% CI.
The colours are here to visually separate the metrics by categories (blue = regularity, yellow = divergence, green = richness); the colour gradient within each row corresponds to a removal of respectively 80\%, 60\%, 40\% and 20\% of the data (from top to bottom).
\textbf{NOTE: for the \texttt{TPD} metrics, the metric is calculated using the 4 first dimensions only.}
}}
\label{Fig:raw_results_emp}
\end{figure}
\bigskip

\begin{figure}[!htbp]
\centering
   \includegraphics{Figures/empirical_data_dimensions.pdf}
\caption{\scriptsize{\textbf{Selection of the number of dimensions for the empirical data:} each histograms corresponds to the variance per dimension (dark grey) and the cumulative variance per dimension (light grey) for each group in the empirical data: the 37 currently endemic Hawaiian species (extant species) the 63 species present before 1500 (pre-1500 group). The plot shows that although 4 dimensions are enough to describe at least 95\% of the variance for the extant group, 5 dimensions are required for the pre-1500 group (following the method proposed in \cite{guillerme2023innovation}).
}}
\label{Fig:empirical_dimensions}
\end{figure}
\bigskip
